\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

\red{In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations. There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop. The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.}

@@

Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid. Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude). Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top r ight-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.

>>>>

\red{ NEEDS TO BE MOVED LATER In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations. There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop. The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.}

@@

\medskip
Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid (\textit{in-situ} hydrocarbons). Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude). Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top r ight-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_2500.pdf} 
            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
      \hbox{\hspace{8.0cm} (a) VR = 1}
      \vspace{1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
      \hbox{\hspace{8.0cm} (b) VR = 10  }}
\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4678$ elements.}
\label{fem_cv_represent_vr1_vr10}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
}
}     
\caption{For $t=0.125$s, $2$ test-cases under the MR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe. The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
}
}     
\caption{For the case of MR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh for the same time steps, t=$0.25$ or t=500(a), t=$0.75$ or t=1500(b). }
\label{fig:4testcase_a}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_2500.pdf} 
            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
      \hbox{\hspace{8.0cm} (a) VR = 1}
      \vspace{1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
      \hbox{\hspace{8.0cm} (b) VR = 10  }}
\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4678$ elements.(\blue{this is a different set of simulation, we might have to change it and bring between the  })}
\label{fem_cv_represent_vr1_vr10}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
}
}     
\caption{For $t=0.125$s, $2$ test-cases under the VR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for VR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe. The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
}
}     
\caption{For the case of VR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh for the same time steps, t=$0.25$ or t=500(a), t=$0.75$ or t=1500(b). }
\label{fig:4testcase_a}
\end{figure}
\end{landscape}
\clearpage
